Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-07-21 main.tex
:pencil: Add active beamforming design

\algrenewcommand{\algorithmicwhile}{\textbf{While}}
\algrenewcommand{\algorithmicif}{\textbf{If}}
\algrenewcommand{\algorithmicthen}{\textbf{Then}}
\algrenewcommand{\algorithmicelse}{\textbf{Else}}
\algrenewcommand{\algorithmicend}{\textbf{End}}
\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
\algrenewcommand{\algorithmicuntil}{\textbf{Until}}

% \floatname{algorithm}{Procedure}
\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
\algrenewcommand{\algorithmicensure}{\textbf{Output:}}

@@

		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and the node $k$-user backward channel as $h_{\mathrm{B},k}$. Also, define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
		% Let $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ be the backscatter symbols of all Metascatters.
		Let $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all Metascatters.
		Consider the signal model during one backscatter block (i.e., $N$ primary blocks).
		% We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
		Under perfect synchronization, the equivalent primary channel is a function of backscatter symbols
		\begin{subequations}
			\label{eq:equivalent_channel}
			\begin{align}
				\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k   \\
				 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
			\end{align}
		\end{subequations}
		where $\alpha_k$ is the amplitude reflect ratio of Metascatter $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the backscatter symbol of Metascatter $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$. The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
		\begin{equation}
			y[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
		\end{equation}
		where $s \sim \mathcal{CN}(0,1)$ is the primary symbol, $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn}, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active beamforming vector with average power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
		% The equivalent channel for primary link is subject to backscatter uncertainty
		% The equivalent primary channel is a function of backscatter symbols  as
		% \begin{equation}
		% 	% \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
		% 	\boldsymbol{h}_{\mathrm{E}}^H(\boldsymbol{x}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}}.
		% 	\label{eq:equivalent_channel}
		% \end{equation}

@@

	\begin{subsection}{Receiving Strategy}
		We propose a Metascatter receiver where the backscatter symbols of all Metascatters are first jointly and semi-coherently detected using total received energy per backscatter block, then modeled within equivalent channel \eqref{eq:equivalent_channel} as dynamic passive beamforming.
		% identified by non-coherent energy detection, then
		% Compared with conventional schemes as joint decoding and \gls{sic}, the Metascatter receiver may not achieve as high data rate for one tag, but it avoids non-coherent primary encoding and enables tag multiple access in a practical and low-complexity manner.
		% Therefore, we believe it can be compatible to and readily implemented over legacy point-to-point systems.
		Compared with \gls{ml} and \gls{sic}, Metascatter receiver allows practical and low-complexity node multiple access with minor adjustment over legacy equipments.

@@

		\begin{remark}
			% For a general input distribution, not only the optimal decision thresholds
			The rate-optimal thresholding channel design remains under-investigated, and some attempts were made for single source with binary inputs in \cite{Qian2019b,Nguyen2021b}.
			% The question was only answered for single source with binary inputs in \cite{Qian2019b,Nguyen2021b}.
			% Some attempts for single source with binary inputs were presented in \cite{Qian2019b,Nguyen2021b}.
			For non-binary inputs with general distribution, the optimal decision region for each letter can be non-convex (i.e., with non-adjacent partitions) and the optimal number of thresholds is still unknown.
			% Next, we will restrict the design over convex decision regions.
			% For a general input distribution, not only the rate-optimal decision thresholds
			% % Interestingly, the optimal threshold design to maximize the mutual information for a general \gls{dmtc} with a fixed number of output letters remains an open issue.
			% % The reason is that each decision region may contain more than one disjoint partitions (i.e., non-convex) and the number of thresholds are unknown.
			% % Fortunately, for the proposed energy detection, we proved that the \gls{dmtc} capacity can be achieved using only convex decision regions.
			% not only the capacity-achieving thresholding design remains an open problem, but also the optimal number of thresholds for general non-binary-input channels remains unknown.
		\end{remark}
		In the following context, we restrict all decision regions to convex and optimize decision thresholds accordingly. That is, for any bijective mapping $f : m_{\mathcal{K}} \to \mathcal{L} \triangleq \{1,\ldots,M^K\}$, the decision region of letter $l \in \mathcal{L}$ is defined as $\mathcal{R}_l \triangleq [t_{l-1},t_l)$, where $t_{l-1}<t_l$. We also define the decision threshold vector as $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^T \in \mathbb{R}_+^{(L+1) \times 1}$.
	\end{subsection}

	\begin{subsection}{Achievable Rates}
		Denote the input probability of state $m_k$ of Metascatter node $k$ as $P_k(x_{m_k})$, and define the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{R}^{M \times 1}$. With independent encoding at all nodes, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
		% Denote the input probability distribution vector of tag $k$ as $\boldsymbol{p}_k \triangleq [P_k(x_1),\ldots,P_k(x_M)]^T \in \mathbb{R}^{M \times 1}$, where $P_k(x_{m_k})$ is the probability at state $m_k$.
		% Consider independent encoding at all tags such that the probability of input combination $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
		% The backscatter information function of input combination $x_{m_{\mathcal{K}}}$ is defined as
		Similar to \cite{Rezaeian2004}, we define the backscatter information function between input symbol tuple instance $x_{m_{\mathcal{K}}}$ and output symbol tuple $\hat{x}_{\mathcal{K}}$ as
		\begin{equation}
			I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})},
			\label{eq:backscatter_information_function}
		\end{equation}
		where $P(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$.
		We also define the backscatter marginal information of letter $x_{m_k}$ of node $k$ as
		% Besides, the backscatter marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			% I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			I^{\mathrm{B}}_{k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			\label{eq:backscatter_marginal_information}
		\end{equation}
		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
		Moreover, we can write the backscatter mutual information as
		\begin{equation}
			% I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})}.
			I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
			\label{eq:backscatter_mutual_information}
		\end{equation}

		% Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.
		Once backscatter symbols are successfully decoded, we can eliminate modulation uncertainty and retrieve equivalent primary channel by \eqref{eq:equivalent_channel}. We define the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ as
		% \begin{equation}
		% 	I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right),
		% 	\label{eq:primary_information_function}
		% \end{equation}
		\begin{equation}
			I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
			\label{eq:primary_information_function}
		\end{equation}
		the primary marginal information conditioned on letter $x_{m_k}$ of node $k$ as
		% the primary marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			I^{\mathrm{P}}_{k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}),
			\label{eq:primary_marginal_information}
		\end{equation}
		and the primary ergodic mutual information as
		% and the primary (ergodic) mutual information is
		\begin{equation}
			% I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right).
			I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}).
			\label{eq:primary_mutual_information}
		\end{equation}

@@

		At each iteration, the input distribution of node $k$ is evaluated over updated input distribution of node $1$ to $k-1$, together with previous input distribution of node $k+1$ to $K$. The \gls{kkt} input distribution design is summarized in Algorithm TODO.

>>>>

\algrenewcommand{\algorithmicwhile}{\textbf{While}}
\algrenewcommand{\algorithmicif}{\textbf{If}}
\algrenewcommand{\algorithmicthen}{\textbf{Then}}
\algrenewcommand{\algorithmicelse}{\textbf{Else}}
\algrenewcommand{\algorithmicend}{\textbf{End}}
\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
\algrenewcommand{\algorithmicuntil}{\textbf{Until}}
\algrenewcommand{\algorithmicdo}{}

% \algrenewcommand\algorithmicdo{}
% \renewcommand\algorithmicdo{}

\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
\algrenewcommand{\algorithmicensure}{\textbf{Output:}}

@@

		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and the node $k$-user backward channel as $h_{\mathrm{B},k}$. Also, define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
		% Let $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ be the backscatter symbols of all Metascatters.
		Let $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all Metascatters.
		Consider the signal model during one backscatter block (i.e., $N$ primary blocks).
		% We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
		Under perfect synchronization, the equivalent primary channel is a function of \emph{coded} backscatter symbols
		\begin{subequations}
			\label{eq:equivalent_channel}
			\begin{align}
				\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k   \\
				 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
			\end{align}
		\end{subequations}
		where $\alpha_k$ is the amplitude reflect ratio of Metascatter $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the coded backscatter symbol of Metascatter $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$. The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
		\begin{equation}
			y[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
		\end{equation}
		where $s \sim \mathcal{CN}(0,1)$ is the primary symbol, $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn}, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active beamforming vector with average power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
		% The equivalent channel for primary link is subject to backscatter uncertainty
		% The equivalent primary channel is a function of backscatter symbols  as
		% \begin{equation}
		% 	% \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
		% 	\boldsymbol{h}_{\mathrm{E}}^H(\boldsymbol{x}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}}.
		% 	\label{eq:equivalent_channel}
		% \end{equation}

@@

	\begin{subsection}{Receiving Strategy}
		We propose a Metascatter receiver where the backscatter messages of all Metascatters are first jointly and semi-coherently detected using total received energy per backscatter block, then modeled within equivalent channel \eqref{eq:equivalent_channel} as dynamic passive beamforming.
		% identified by non-coherent energy detection, then
		% Compared with conventional schemes as joint decoding and \gls{sic}, the Metascatter receiver may not achieve as high data rate for one tag, but it avoids non-coherent primary encoding and enables tag multiple access in a practical and low-complexity manner.
		% Therefore, we believe it can be compatible to and readily implemented over legacy point-to-point systems.
		Compared with \gls{ml} and \gls{sic}, Metascatter receiver allows practical and low-complexity node multiple access with minor adjustment over legacy equipments.

@@

		\begin{remark}
			% For a general input distribution, not only the optimal decision thresholds
			The rate-optimal thresholding channel design remains under-investigated, and some attempts were made for single source with binary inputs in \cite{Qian2019b,Nguyen2021b}.
			% The question was only answered for single source with binary inputs in \cite{Qian2019b,Nguyen2021b}.
			% Some attempts for single source with binary inputs were presented in \cite{Qian2019b,Nguyen2021b}.
			For non-binary inputs with general distribution, the optimal decision region for each letter can be non-convex (i.e., with non-adjacent partitions) and the optimal number of thresholds is still unknown.
			% Next, we will restrict the design over convex decision regions.
			% For a general input distribution, not only the rate-optimal decision thresholds
			% % Interestingly, the optimal threshold design to maximize the mutual information for a general \gls{dmtc} with a fixed number of output letters remains an open issue.
			% % The reason is that each decision region may contain more than one disjoint partitions (i.e., non-convex) and the number of thresholds are unknown.
			% % Fortunately, for the proposed energy detection, we proved that the \gls{dmtc} capacity can be achieved using only convex decision regions.
			% not only the capacity-achieving thresholding design remains an open problem, but also the optimal number of thresholds for general non-binary-input channels remains unknown.
		\end{remark}
		In the following context, we restrict all decision regions to convex and optimize decision thresholds accordingly. That is, for any bijective mapping $f : m_{\mathcal{K}} \to \mathcal{L} \triangleq \{1,\ldots,M^K\}$, the decision region of letter $l \in \mathcal{L}$ is defined as $\mathcal{R}_l \triangleq [t_{l-1},t_l)$, where $t_{l-1} \le t_l$. We also define the decision threshold vector as $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^T \in \mathbb{R}_+^{(L+1) \times 1}$.
	\end{subsection}

	\begin{subsection}{Achievable Rates}
		Denote the input probability of state $m_k$ of Metascatter node $k$ as $P_k(x_{m_k})$, and define the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{R}^{M \times 1}$. With independent encoding at all nodes, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
		\begin{equation}
			P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k}).
			\label{eq:equivalent_distribution}
		\end{equation}
		% Denote the input probability distribution vector of tag $k$ as $\boldsymbol{p}_k \triangleq [P_k(x_1),\ldots,P_k(x_M)]^T \in \mathbb{R}^{M \times 1}$, where $P_k(x_{m_k})$ is the probability at state $m_k$.
		% Consider independent encoding at all tags such that the probability of input combination $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
		% The backscatter information function of input combination $x_{m_{\mathcal{K}}}$ is defined as
		Similar to \cite{Rezaeian2004}, we define the backscatter information function between input symbol tuple instance $x_{m_{\mathcal{K}}}$ and output symbol tuple $\hat{x}_{\mathcal{K}}$ as
		\begin{equation}
			I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})},
			\label{eq:backscatter_information_function}
		\end{equation}
		where $P(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$.
		We also define the backscatter marginal information of letter $x_{m_k}$ of node $k$ as
		% Besides, the backscatter marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			% I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			I^{\mathrm{B}}_{k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			\label{eq:backscatter_marginal_information}
		\end{equation}
		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
		Moreover, we can write the backscatter mutual information as
		\begin{equation}
			% I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})}.
			I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
			\label{eq:backscatter_mutual_information}
		\end{equation}

		% Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.

		% eliminate modulation uncertainty
		Once backscatter messages are successfully decoded, we can re-encode to determine $x_{\mathcal{K}}$ and retrieve equivalent primary channel by \eqref{eq:equivalent_channel}. We define the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ as
		% Once backscatter symbols are successfully decoded, we can eliminate modulation uncertainty and retrieve equivalent primary channel by \eqref{eq:equivalent_channel}. We define the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ as
		% \begin{equation}
		% 	I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right),
		% 	\label{eq:primary_information_function}
		% \end{equation}
		\begin{equation}
			I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
			\label{eq:primary_information_function}
		\end{equation}
		the primary marginal information conditioned on letter $x_{m_k}$ of node $k$ as
		% the primary marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			I^{\mathrm{P}}_{k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}),
			\label{eq:primary_marginal_information}
		\end{equation}
		and the primary ergodic mutual information as
		% and the primary (ergodic) mutual information is
		\begin{equation}
			% I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right).
			I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}).
			\label{eq:primary_mutual_information}
		\end{equation}

@@

		At each iteration, the input distribution of node $k$ is evaluated over updated input distribution of node $1$ to $k-1$, together with previous input distribution of node $k+1$ to $K$. The \gls{kkt} input distribution design is summarized in Algorithm \ref{al:input_distribution}.

		\begin{algorithm}[!t]
			\caption{Numerical Evaluation of \gls{kkt} Input Distribution}
			\label{al:input_distribution}
			\begin{algorithmic}[1]
				\Require $K$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
				\State Set $\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
				\State \phantom{Set} $f(z|\mathcal{H}_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
				\State \phantom{Set} $P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dtmac}
				\State Initialize $r \gets 0$
				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
				\State Get $P_{\mathcal{K}}^{(0)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
				\State \phantom{Get} $I^{(0)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
				\State \phantom{Get} $I^{(0)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
				\State \phantom{Get} $I^{(0)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information}
				\Repeat
					\State Update $r \gets r+1$
					\State \phantom{Update} $\boldsymbol{p}_k^{(r)}$, $\forall k$ by \eqref{eq:input_kkt_solution}
					\State Get $P_{\mathcal{K}}^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
					\State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
					\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
					\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information}
				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \epsilon$
			\end{algorithmic}
		\end{algorithm}
	\end{subsection}
